### 2021-07-20 chapters/7_experiment_design.tex
ping

\documentclass[../main]{subfiles}
\begin{document}
\chapter{Experiment design}
In this chapter we design an experiment to validate our research.
We will execute the following steps:
\begin{enumerate}
    \item Gather all characteristics from PIT.
    \item Execute full set of mutants to gather baseline measurement.
    \item Cluster the mutants according the black and white box methodologies.
    \item Execute one random mutant per cluster and gather result.
    \item Calculate weighted mutation score.
\end{enumerate}
We hypothesise that we can cluster mutants with the set of characteristics we identified
while maintaining effectiveness and reducing the amount executed when executing one mutant from each cluster that is randomly selected.
Our goal is to achieve a weighted mutation score that is as close as possible to the mutation score of a full set of executed mutants.
We will repeat the experiment for each approach we devised in Chapters \ref{ch:reserach_question1} and \ref{ch:reserach_question2}.

@@

\section{Validation}
\label{ch:exp1_validation}
The most efficient way to measure test effectiveness with mutation testing is by executing all mutants that a mutation testing tool can possibly generate.
The goal of this research is to reduce the amount of mutants executed while maintaining effectiveness.
To reduce the amounts executed we cluster the mutants. 
We can measure this by counting the number of clusters we generate and compare it to the number of total mutants generated by the selected tool.
\newline
To validate how effective our method of clustering is we can compare the weighted mutation score(see Chapter \ref{ch:weighted_score}) of the clustered set to the mutation score of the full set.
The closer the weighted score is to that of a full set the more effective our set of characteristics and clustering algorithm proves to be.
In other words we want achieve a mutation score that is as close as possible as to that of a full set.
We select a statistical significance level of $\leq 0.05$.
This is the conventional threshold for declaring statistical significance\cite{Kirk1996PracticalCome}.
\newline
Depending on the effectiveness of our clustering algorithm we may loose accuracy.
This can happen if a cluster contains mutants of both results. 
We can measure the accuracy inside a cluster by calculating a percentage of all mutants that have survived against the ones that have been killed in a cluster.
If the majority of the mutants in a cluster is killed then we consider that cluster to represent a killed cluster and the other way around for survived mutants.
We consider the mutants that are not in the majority of the cluster as inaccuracy.
\newline
If the weighted mutation score of our clustered set deviates more than 5\% from the score of a full set we will reject our hypothesis.

>>>>

\documentclass[../main]{subfiles}
\begin{document}
\chapter{Experiment design}
In this chapter we design an experiment to validate our research.
We will execute the following steps:
\begin{enumerate}
    \item Gather all mutant characteristics from PIT.
    \item Execute full set of mutants to gather baseline measurement.
    \item Cluster the mutants according the black and white box methodologies.
    \item Execute one random mutant per cluster and gather result.
    \item Calculate weighted mutation score.
\end{enumerate}
We hypothesise that we can cluster mutants with the set of characteristics we identified
while maintaining effectiveness and reducing the amount executed when executing one mutant from each cluster that is randomly selected.
Our goal is to achieve a weighted mutation score that is as close as possible to the mutation score of a full set of executed mutants.
We will repeat the experiment for each approach we devised in Chapters \ref{ch:reserach_question1} and \ref{ch:reserach_question2}.

@@

\section{Validation}
\label{ch:exp1_validation}
The most efficient way to measure test effectiveness with mutation testing is by executing all mutants that a mutation testing tool can possibly generate.
The goal of this research is to reduce the amount of mutants executed while maintaining effectiveness.
To reduce the amounts executed we cluster the mutants. 
We can measure this by counting the number of clusters we generate and compare it to the number of total mutants generated by the selected tool.
\newline
To validate how effective our method of clustering is we can compare the weighted mutation score(see Chapter \ref{ch:weighted_score}) of the clustered set to the mutation score of the full set.
The closer the weighted score is to that of a full set the more effective our set of characteristics and clustering algorithm proves to be.
In other words we want achieve a mutation score that is as close as possible as to that of a full set.
We select a statistical significance level of $\leq 0.05$.
This is the conventional threshold for declaring statistical significance\cite{Kirk1996PracticalCome}.
\newline
Depending on the effectiveness of our clustering algorithm we may loose accuracy.
This can happen if a cluster contains mutants of both results. 
We can measure the accuracy inside a cluster by calculating a percentage of all mutants that have survived against the ones that have been killed in a cluster.
If the majority of the mutants in a cluster is killed then we consider that cluster to represent a killed cluster and the other way around for survived mutants.
We consider the mutants that are not in the majority of the cluster as inaccuracy.
\newline
If the weighted mutation score of our clustered set deviates more than 5\% from the score of a full set we reject our hypothesis.
